\documentclass{article}
\usepackage{graphicx}
\usepackage{hyperref}

\begin{document}

Logan
8 INCH SHAPER
Operation
INSTRUCTIONS
and
Parts List

HOW TO ORDER REPAIR PARTS

Should you need repair parts for your shaper the following information
is necessarey to fill your order promptly and correctly.

Complete name and number of the parts as listed in the parts list.

Model and serial number of your shaper.

The serial number is located on the upper portion of the main frame
near the right hand end of machine.  The model number is stamped on
the name plate located on the upper left-hand side.

Please place your order through the Logan Dealer from whom you
obtained the shaper.

LOGAN ENGINEERING CO. CHICAGO 30, ILL.

\page

\picture

LOGAN\n8 INCH SHAPER

\page

OPERATING INSTRUCTIONS

The Logan Shaper is carefully packed and bound in a sturdy crate for
safe arrival in perfect working condition.  It arrives completely
assembled, ready for operation.  The motor, too, if ordered with the
shaper, is ready for service.  The shaper and motor are thoroughly
lubricated at the factory, and all machined surfaces are grease coated
to prevent rust while in stock and transit.

\subsection{SETTING UP}

Mount the shaper on a solid, level space to eliminate the possibility
of vibration.  Level the shaper lengthwise and crosswise.  Use shims
if necessary to obtain a level, firm foundation.

Fasten the shaper firmly to the floor with bolts or lag screws.

Wipe off excess grease and clean the machine with kerosene or similar
substance.

Before operating the machine for any length of time, lubricate it
thoroughly at all points indicated by the lubrication chart.

\subsection{MOTOR MOUNTING AND BELT TENSIONING}

If motor is ordered with the shaper, it is factory mounted on the
motor bracket and wired to the switch with cord extending through the
base of the shaper for electrical outlets.

If the motor is not ordered with the shaper, or if, for special
reason, it is not mounted at the factory, it becomes necessary to
drill four holes to accommodate the motor base.

Belt adjustment is made by means of two bolts extending through the
rear of the base.  Belt tension is increased by loosening the lower
bolt and tightening the upper bolt.  Reversing this procedure
decreases belt tension.

\subsection{HOLDING WORK}

The exceptionally large table of the Logan Shaper is designed for easy
mounting of all types of work pieces.  Top and side surfaces have
three ``T'' slots each to permit secure fastening of clamps or
fixtures.  Its heavy-ribbed, sturdy vise is fastened to the table by
square head bolts in T-Slots.  The vise is mounted on a swivel and
calibrated from 0\degrees to 90\degrees right and left.  Opening
capacity of the vise is 5\inch and jaws measure 1\half\inch by 5\inch.

\subsection{STROKE ADJUSTMENT}

Measure work to determine length of stroke required.  Allow
approximately \quarter\inch extra for tool clearance.

By means of crank, run ram to furthermost return position.

On left hand side of shaper open small door thus exposing crank pin
stud.

Loosen crank pin stud by turning right (left hand thread.)

Loosen crank pin stud located on top and center of ram.

Push ram manually until stroke indicator shows desired length of
stroke (plus \quarter\inch extra allowance) on stroke indicator plate.

Tighten crank pin studs on stroke adjuster and stroke indicator.

Test stroke with crank before applying power to make certain that the
ram does not strike front of shaper frame.

\subsection{LOCATING RAM POSITION}

Loosen stroke indicator.

Push ram manually until ram is in proper position to over work.

Tighten stroke indicator and manually test stroke once more.

\subsection{TOOL HEAD}

The tool head is mounted on the front of the ram.

It is mounted on a swivel and rotates 45\degrees to right and left of
its upright position.  To change position of tool holder loosen two
hex head cap screws holding swivel.  Turn head to desired degree of
rotation and tighten securely.

\subsection{CLAPPER BOX}

The clapper box on the Logan Shaper can be rotated to left or right by
loosening a single hex head cap screw.  The clapper is mounted within
the clapper box on a pivot pin.  This arrangement permits the tool bit
to clear the work on the return stroke with minimum interference.
Immediately after the tool bit clears the work on the return stroke,
the clapper hold-down returns the clapper to its operating position.

To remove or change the tool holder, turn the knurled half nut on the
clapper hold-down, in this way releasing spring tension.

\subsection{TABLE ADJUSTMENTS}

The Logan Shaper table is easily adjustable both horizontally and
vertically. Horizontal adjustment is made by use of the crank pin stud
extending out from the right side at the rear of the table.  Maximum
horizontal movement is 11\half\inch

To make vertical adjustment, a conveniently located crank permits
quick raising and lowering of the table.  Loosen the top and bottom
gib nuts on the right side of the table ways.  Turn the crank to the
right to raise the table, or to the left to lower the table.  When the
table reaches the desired position, tighten the gib locks.  Maximum
vertical movement is 5\half\inch.

\subsection{FEED}

The Logan Shaper feed is reversible and adjustable.  One tooth on the
ratchet is equal to a cross feed of 0.002\inch.  There are six
automatic feeds in either direction.  They are 0.002\inch, 0.004\inch,
0.006\inch, 0.008\inch, 0.010\inch, and 0.012\inch.

A one-quarter turn of the feed handle will disengage the feed, while
an additional quarter-turn will again engage the feed, but in the
opposite direction.  Consequently, a half-turn of the handle reverses
the feed.

\end{document}

% LocalWords:  tensioning shaper gib

